Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2023-01-30 reports/supplement/supplement_0.9.1.Rmd
revised figure 11.1

          (num_strains == -1 & var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "SB" & stand_var > 0.60) ~ "non-standard",
          (num_strains == -1 & var_treat == "PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-SB" & stand_var > 0.60) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  ) %>%
  mutate(hyst_min_log = ifelse(var_treat == "CB-SB" &
                                 stab_states_type == "non-standard" &
                                 Species == "SB_tot" &
                                 stand_var > 0.85,
                               -8,
                               hyst_min_log
                                 ))

>>>>

          (num_strains == -1 & var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "SB" & stand_var > 0.60) ~ "non-standard",
          (num_strains == -1 & var_treat == "PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-SB" & stand_var > 0.60) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  ) %>%
  mutate(hyst_min_log = ifelse(var_treat == "CB-SB" &
                                 stab_states_type == "non-standard" &
                                 Species == "SB_tot" &
                                 stand_var > 0.85,
                               -8,
                               hyst_min_log
                                 ),
         hyst_max_log = ifelse(var_treat == "CB-SB" &
                                 stab_states_type == "non-standard" &
                                 Species == "SB_tot" &
                                 stand_var > 0.85,
                               -8,
                               hyst_max_log
                                 ))
